### 2025-10-28 Text/Thesis/Chapters/Chapter2.qmd
Corrected figures

Figures&nbsp;[-@fig-shannon-convergence-s]--[-@fig-tsallis-convergence-t] illustrate the Shannon ($H$), Rényi ($R_\lambda$), and Tsallis ($T_\lambda$) entropies for the $\mathcal{G}^0_I$ model under different texture levels ($\alpha$) and numbers of looks ($L$).  In every case the coloured dashed curves converge to the solid black baseline of the homogeneous $\Gamma_{\mathrm{SAR}}$ distribution as $\alpha\to-\infty$, confirming the limiting behavior.

For the Shannon entropy (@fig-shannon-convergence-s), when $L = 5$ the entropy curves for different $\alpha$ values are more concentrated. This is due to the higher speckle noise present in a low number of looks, which dominates the uncertainty and masks texture effects. When $L = 18$, speckle is reduced and the entropy better reflects texture variation, resulting in more separated curves.

In the case of Rényi entropy (@fig-renyi-convergence-r), for $\lambda = 0.6$ and $\lambda = 0.9$, the general shape and separation of the curves are similar. However, increasing $L$ leads to a slight decrease in entropy values across all $\alpha$, consistent with reduced speckle. The convergence pattern toward the Gamma baseline remains stable in both settings.

For Tsallis entropy (@fig-tsallis-convergence-t), the separation between curves is most noticeable for $\lambda = 0.6$ and $L = 5$, where texture has more influence. When $\lambda$ increases to $0.9$ or when $L$ is increased, the curves become more compact and approach the Gamma entropy faster, indicating lower sensitivity to texture variation and confirming that $\lambda$ controls the influence of the tail behavior.

```{r fig-shannon-convergence-s, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}

@@

```{r fig-renyi-convergence-r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
# fig.fullwidth = TRUE, out.width="95%"

@@

```{r fig-tsallis-convergence-t, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="98%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
# fig.fullwidth = TRUE, out.width="95%"

@@

>>>>

Figures&nbsp;\ref{fig-shannon-convergence-s}--\ref{fig-tsallis-convergence-t} illustrate the Shannon ($H$), Rényi ($R_\lambda$), and Tsallis ($T_\lambda$) entropies for the $\mathcal{G}^0_I$ model under different texture levels ($\alpha$) and numbers of looks ($L$).  In every case the coloured dashed curves converge to the solid black baseline of the homogeneous $\Gamma_{\mathrm{SAR}}$ distribution as $\alpha\to-\infty$, confirming the limiting behavior.

For the Shannon entropy (Figure&nbsp;\ref{fig-shannon-convergence-s}), when $L = 5$ the entropy curves for different $\alpha$ values are more concentrated. This is due to the higher speckle noise present in a low number of looks, which dominates the uncertainty and masks texture effects. When $L = 18$, speckle is reduced and the entropy better reflects texture variation, resulting in more separated curves.

In the case of Rényi entropy (Figure&nbsp;\ref{fig-renyi-convergence-r}), for $\lambda = 0.6$ and $\lambda = 0.9$, the general shape and separation of the curves are similar. However, increasing $L$ leads to a slight decrease in entropy values across all $\alpha$, consistent with reduced speckle. The convergence pattern toward the Gamma baseline remains stable in both settings.

For Tsallis entropy (Figure&nbsp;\ref{fig-tsallis-convergence-t}), the separation between curves is most noticeable for $\lambda = 0.6$ and $L = 5$, where texture has more influence. When $\lambda$ increases to $0.9$ or when $L$ is increased, the curves become more compact and approach the Gamma entropy faster, indicating lower sensitivity to texture variation and confirming that $\lambda$ controls the influence of the tail behavior.

```{r fig-shannon-convergence-s,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}

@@

```{r fig-renyi-convergence-r,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
# fig.fullwidth = TRUE, out.width="95%"

@@

```{r fig-tsallis-convergence-t,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="98%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
# fig.fullwidth = TRUE, out.width="95%"

@@

```{=latex}
\begin{figure}[hbt]

\caption{\label{fig-shannon-convergence-s}Shannon entropy
\(H(\mathcal{G}^0_I)\) converges to \(H(\Gamma_{\mathrm{SAR}})\) as
\(\alpha\) decreases.}

\centering{

\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-shannon-convergence-s-1.pdf}

\end{figure}%

\begin{figure}[hbt]

\caption{\label{fig-renyi-convergence-r}Rényi entropy
\(R_{\lambda}(\mathcal{G}^0_I)\) converges to
\(R_{\lambda}(\Gamma_{\mathrm{SAR}})\) as \(\alpha\) decreases.}

\centering{

\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-renyi-convergence-r-1.pdf}

\end{figure}%

\begin{figure}[H]

\caption{\label{fig-tsallis-convergence-t}Tsallis entropy
\(T_{\lambda}(\mathcal{G}^0_I)\) converges to
\(T_{\lambda}(\Gamma_{\mathrm{SAR}})\) as \(\alpha\) decreases.}

\centering{

\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-tsallis-convergence-t-1.pdf}

\end{figure}%
```

### 2025-10-28 Text/Thesis/Chapters/Chapter3.qmd
Corrected figures

For the Rényi estimator (see Fig. \ref{fig-optimal_order}), $\lambda = 0.9$ minimizes the MSE while keeping the bias low, achieving a favorable bias-variance trade-off. Although $\lambda = 0.85$ yields slightly lower bias, it produces a higher MSE, supporting the choice of $\lambda = 0.9$ as optimal.

Similarly, for the Tsallis estimator (Fig. \ref{fig-optimal_order-tsallis}), $\lambda = 0.85$ results in the lowest MSE with moderate bias, making it the most suitable choice.

@@

```{r fig-optimal_order,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r fig-optimal_order-tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```
<!-- ```{=latex} -->
<!-- \begin{figure}[hbt] -->
<!--   \centering -->
<!--   \includegraphics[width=0.42\textwidth]{Figures-R1/fig-optimal_order-1.pdf} -->
<!--   \vspace{0.5em} -->
<!--   \caption{Bias and MSE as a function of $\lambda$, with $n=49$, $L=5$.} -->
<!--   \label{fig-optimal_order} -->
<!-- \end{figure} -->
<!-- ``` -->
\vspace{-15pt}
In the case of $L = 1$, the bootstrap procedure does not provide meaningful improvement and often leads to unstable estimates. Therefore, we omit bootstrap in this setting. Under these conditions, higher values of $\lambda$ yield better results: $\lambda = 3$ is preferred for the Rényi estimator, and $\lambda = 1.2$ for the Tsallis estimator. 
\vspace{-15pt}

@@

Building upon the previous Monte Carlo setup, we further assess the performance of the Rényi and Tsallis entropy estimators by analyzing their behavior across varying sample sizes $n \in \{9, 25, 49, 81, 121\}$. Using the optimal values of the order parameter ($\lambda = 0.9$ for Rényi and $\lambda = 0.85$ for Tsallis) already identified in the earlier analysis, we compute the bias and MSE for both the original and bootstrap-corrected versions of the estimators. As illustrated in Figures&nbsp;\ref{fig-bias_mse_rm1} and \ref{fig-bias_mse_Tsallis}, the bootstrap estimators consistently show improved performance for small samples. 
\vspace{-10pt}
```{r Simulated_data_bias_m1, echo=FALSE, message=FALSE }
set.seed(1234567890, kind = "Mersenne-Twister")
#cache = TRUE, autodep = TRUE

@@

```{r fig-bias_mse_rm1,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.5}

@@

```{r Simulated_data_bias_tt, echo=FALSE, message=FALSE }
set.seed(1234567890, kind = "Mersenne-Twister")
#cache = TRUE, autodep = TRUE

@@

```{r fig-bias_mse_Tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="htb",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.6}

@@

@@

Figures [-@fig-densities-shannon]-[-@fig-densities-tsallis4] display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.

@@

```{r Simulated_density-shannon, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

```{r Simulated_densityR, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r Simulated_density-tsallis2, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

Under the asymptotic properties of the entropy estimators [@vasicek1976test;@VanEs1992], for sufficiently large samples, $S_{\widetilde{\theta}}(\bm{Z};L)$ follows an asymptotic normal distribution:
<!-- From the asymptotic theory of entropy estimators [@vasicek1976test;@VanEs1992], we know that for sufficiently large samples the statistic $S_{\widetilde{\theta}}(\bm{Z};L)$ converges in distribution to a normal law. Formally, as: -->
$$
  S_{\widetilde{\theta}}(\mathbf Z;L)\;
  \overset{\mathcal{D}}{\underset{n \to \infty}{\longrightarrow}}\;
  \mathcal N\!\bigl(\mu_S,\sigma_S^{2}\bigr),
$$
where ${\widetilde{\theta}\in\{\widetilde{H},\;\widetilde{R}_\lambda,\;\widetilde{T}_\lambda\}}$  and $\xrightarrow{\mathcal{D}}$ denotes convergence in distribution.

@@

The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures. These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;@fig-compare_size_power_plot0.

@@

As expected, power increased with both the sample size and the number of looks. This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;@fig-compare_size_power_plot0.

@@

```{r fig-compare_size_power_plot0, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies. Size and Power for different sample sizes and $L$ values."}
library(ggplot2)

@@

>>>>

For the Rényi estimator (see Figure&nbsp;\ref{fig-optimal_order}), $\lambda = 0.9$ minimizes the MSE while keeping the bias low, achieving a favorable bias-variance trade-off. Although $\lambda = 0.85$ yields slightly lower bias, it produces a higher MSE, supporting the choice of $\lambda = 0.9$ as optimal.

Similarly, for the Tsallis estimator (Figure&nbsp;\ref{fig-optimal_order-tsallis}), $\lambda = 0.85$ results in the lowest MSE with moderate bias, making it the most suitable choice.

@@

```{r fig-optimal_order, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r fig-optimal_order-tsallis,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{=latex}
\begin{figure}[htb]

\caption{\label{fig-optimal_order}Bias and MSE as a function of
\(\lambda\), for the Rényi entropy estimator, with \(n = 49\),
\(L = 5\).}

\centering{

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{Figures/fig-optimal_order-1.pdf}

}

\end{figure}%

\begin{figure}[htb]

\caption{\label{fig-optimal_order-tsallis}Bias and MSE as a function of
\(\lambda\), for the Tsallis entropy estimator, with \(n = 49\),
\(L = 5\).}

\centering{

\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{Figures/fig-optimal_order-tsallis-1.pdf}

}

\end{figure}%
```

<!-- ```{=latex} -->
<!-- \begin{figure}[hbt] -->
<!--   \centering -->
<!--   \includegraphics[width=0.42\textwidth]{Figures-R1/fig-optimal_order-1.pdf} -->
<!--   \vspace{0.5em} -->
<!--   \caption{Bias and MSE as a function of $\lambda$, with $n=49$, $L=5$.} -->
<!--   \label{fig-optimal_order} -->
<!-- \end{figure} -->
<!-- ``` -->
\vspace{-15pt}
In the case of $L = 1$, the bootstrap procedure does not provide meaningful improvement and often leads to unstable estimates. Therefore, we omit bootstrap in this setting. Under these conditions, higher values of $\lambda$ yield better results: $\lambda = 3$ is preferred for the Rényi estimator, and $\lambda = 1.2$ for the Tsallis estimator. 
\vspace{-15pt}

@@

Building upon the previous Monte Carlo setup, we further assess the performance of the Rényi and Tsallis entropy estimators by analyzing their behavior across varying sample sizes $n \in \{9, 25, 49, 81, 121\}$. Using the optimal values of the order parameter ($\lambda = 0.9$ for Rényi and $\lambda = 0.85$ for Tsallis) already identified in the earlier analysis, we compute the bias and MSE for both the original and bootstrap-corrected versions of the estimators. As illustrated in Figures&nbsp;\ref{fig-bias_mse_rm1} and \ref{fig-bias_mse_Tsallis}, the bootstrap estimators consistently show improved performance for small samples. 
\vspace{-10pt}
```{r Simulated_data_bias_m1,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE }
set.seed(1234567890, kind = "Mersenne-Twister")
#cache = TRUE, autodep = TRUE

@@

```{r fig-bias_mse_rm1,   eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.5}

@@

```{r Simulated_data_bias_tt,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE }
set.seed(1234567890, kind = "Mersenne-Twister")
#cache = TRUE, autodep = TRUE

@@

```{r fig-bias_mse_Tsallis,  eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="htb",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.6}

@@

```{=latex}
\begin{figure}[H]

\caption{\label{fig-bias_mse_rm1}Bias and MSE of the Rényi entropy
estimators for \(\Gamma_{\text{SAR}}\), with \(L=5\)}

\centering{

\includegraphics[width=0.65\linewidth,height=\textheight,keepaspectratio]{Figures/fig-bias_mse_rm1-1.pdf}

}

\end{figure}%

\begin{figure}[htb]

\caption{\label{fig-bias_mse_Tsallis}Bias and MSE of the Tsallis entropy
estimators for \(\Gamma_{\text{SAR}}\), with \(L=5\)}

\centering{

\includegraphics[width=0.65\linewidth,height=\textheight,keepaspectratio]{Figures/fig-bias_mse_Tsallis-1.pdf}

}

\end{figure}%
```

@@

Figures&nbsp;\ref{fig-densities-shannon}-\ref{fig-densities-tsallis4} display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.

@@

```{r Simulated_density-shannon, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities-shannon, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

```{r Simulated_densityR, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities, eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r Simulated_density-tsallis2, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r fig-densities-tsallis4, eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{=latex}
\begin{figure}[hbt]

\caption{\label{fig-densities-shannon}Empirical densities of
\(S_{\widetilde{H}_{AO}}(\bm{Z}; L)\) under \(\mathcal{H}_0\).}

\centering{

\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-shannon-1.pdf}

}

\end{figure}%

\begin{figure}[hbt]

\caption{\label{fig-densities}Empirical densities of
\(S_{\widetilde{R}_{\lambda}}(\bm{Z}; L)\) under \(\mathcal{H}_0\), with
\(\lambda=0.9\).}

\centering{

\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-1.pdf}

}

\end{figure}%

\begin{figure}[H]

\caption{\label{fig-densities-tsallis4}Empirical densities of
\(S_{\widetilde{T}_{\lambda}}(\bm{Z}; L)\) under \(\mathcal{H}_0\), with
\(\lambda=0.85\).}

\centering{

\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-tsallis4-1.pdf}

}

\end{figure}%
```
Under the asymptotic properties of the entropy estimators [@vasicek1976test;@VanEs1992], for sufficiently large samples, $S_{\widetilde{\theta}}(\bm{Z};L)$ follows an asymptotic normal distribution:
<!-- From the asymptotic theory of entropy estimators [@vasicek1976test;@VanEs1992], we know that for sufficiently large samples the statistic $S_{\widetilde{\theta}}(\bm{Z};L)$ converges in distribution to a normal law. Formally, as: -->
$$
  S_{\widetilde{\theta}}(\mathbf Z;L)\;
  \overset{\mathcal{D}}{\underset{n \to \infty}{\longrightarrow}}\;
  \mathcal N\!\bigl(\mu_S,\sigma_S^{2}\bigr),
$$
where ${\widetilde{\theta}\in\{\widetilde{H},\;\widetilde{R}_\lambda,\;\widetilde{T}_\lambda\}}$  and $\xrightarrow{\mathcal{D}}$ denotes convergence in distribution.

@@

The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures. These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

As expected, power increased with both the sample size and the number of looks. This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

```{r fig-compare_size_power_plot0,  eval=FALSE,  include=FALSE, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies. Size and Power for different sample sizes and $L$ values."}
library(ggplot2)

@@

```{=latex}
\begin{figure}[H]

\caption{\label{fig-compare_size_power_plot0}Comparative performance of
test statistics based on Shannon, Rényi and Tsallis entropies. Size and
Power for different sample sizes and \(L\) values.}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{Figures/fig-compare_size_power_plot0-1.pdf}}

}

\end{figure}%
```
